Water desalination using polyelectrolyte hydrogel: Gibbs ensemble modeling

### 2022-09-14 gibbs.tex
Update gibbs.tex

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{Recently polyelectrolyte hydrogels have been proposed as draw agents for the forward osmosis desalination techniques. 
Indeed, polyelectrolyte hydrogels have the ability to absorb a big amount of water across an osmosis membrane as a result of their swelling pressure. 
On the other hand, the insoluble cross-linked network of the gel enables dewatering under the influence of a stimulus (thermal and/or mechanical).
Moreover, from a thermodynamic perspective, the polyelectrolyte hydrogel is already an osmotic membrane rejecting ions between external and internal solutions.
These three properties of the gels make it possible to use them for desalination and at the same time avoid the use of expensive membranes.

In this article, we present our recent theoretical study of the usage of polyelectrolyte hydrogel for water desalination. 
Using coarse-grained model and the Gibbs ensemble, we modeled the thermodynamic equilibrium between coexisting phases of the gel and corresponding supernate aqueous 
salt solution.

We performed a sequence of step-by-step hydrogel compressions in \emph{open} and \emph{closed} systems.
The compression in \emph{open system} causes the decrease of salt ions inside the hydrogel,
while the compression in \emph{clesed system} causes the decrease of the supernatant solution.
We modeled this stepwise process of continuous decrease of seawater salinity up to freshwater concentrations.
We estimated the energy costs of the entire process as 38.2 J per production of 1 liter of potable water, which is comparable with reverse osmosis.
}

>>>>

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{Recently, polyelectrolyte hydrogels have been proposed as draw agents for the forward osmosis desalination techniques. 
Indeed, polyelectrolyte hydrogels have the ability to absorb a big amount of water across an osmosis membrane as a result of their swelling pressure. 
On the other hand, the insoluble cross-linked hydrogel network enables dewatering under the influence of external (thermal and/or mechanical) stimulus.
Moreover, from a thermodynamic perspective, the polyelectrolyte hydrogel is already an osmotic membrane.
These above mentioned hydrogel properties designates them as excellent candidates for desalination, and, at the same time, avoid the use of expensive membranes.
In this article, we present our recent theoretical study of polyelectrolyte hydrogel usage for water desalination. 
Employing coarse-grained model and the Gibbs ensemble, we modeled the thermodynamic equilibrium between coexisting gel phase and supernate aqueous salt solution phase.
We performed a sequence of step-by-step hydrogel compressions in \emph{open} and \emph{closed} systems.
The compression in \emph{open system} causes the decrease of salt ions inside the hydrogel,
while the compression in \emph{clesed system} causes the decrease of the salt concentration in the supernatant solution.
We modeled this stepwise process of continuous decrease of water salinity from seawater up to freshwater concentrations.
We estimated the energy costs of the entire process as 38.2 J per production of 1 liter of potable water, which is comparable with reverse osmosis.
}
